\cvsection{Education}
\begin{cventries}
  \cventry
  {Doctoral Program in Computer Science}
  {Universidade do Porto}
  {Porto, Portugal}
  {Oct. 2023 - PRESENT}
  {
    \begin{cvitems}
      \item {Demonstrating security of post-quantum schemes and researching post-quantum migration of systems through the design, security proofs, verification and validation of optimized high-assurance implementations and specifications of PQC and hybrid protocols in the eAuthentication domain.
      The first publication was a collaborative process that lead to the introduction and rigorous security proofs a practical and efficient hybrid KEM to use during post-quantum migration. It has been submitted as an Internet-Draft to the IETF.}
    \end{cvitems}
  }
  \cventry
  {Information Security MSc}
  {Royal Holloway, University of London}
  {Egham, United Kingdom}
  {Sep. 2018 - Sept. 2019}
  {
    \begin{cvitems}
      \item {Achieved a high level Distinction (86\%).}
    \end{cvitems}
  }
  \cventry
  {Computer Science BSc (Hons)}
  {University of Bath}
  {Bath, United Kingdom}
  {Sep. 2015 - Jul. 2018}
  {
    \begin{cvitems}
      \item {Achieved a First Class with Honours (70\%).}
    \end{cvitems}
  }
  \cventry
  {International Baccalaureate}
  {St. Julian's School}
  {Carcavelos, Portugal}
  {Sep. 2013 - Jun. 2015}
  {
    \begin{cvitems}
      \item{Maths HL: 6 | Computer Science HL: 6 | Physics HL: 5 | English Literature and Language SL: 6 | Business and Management SL: 6 | French B SL: 6.}
    \end{cvitems}
  }
\end{cventries}