\cvsection{Experience}
\begin{cventries}
  \cventry
  {Researcher}
  {INESC-TEC}
  {Porto, Portugal}
  {Mar. 2024 - present}
  {
    \begin{cvitems}
      \item{Working as a researcher within HASLAB.}
    \end{cvitems}
  }
  \cventry
  {Junior Crypto Specialist}
  {TNO}
  {The Hague, Netherlands}
  {Aug. 2021 - Aug. 2023}
  {
    \begin{cvitems}
      \item{Worked within the Applied Crypto \& Quantum Algorithms group where we applied the latest academic research to solve real-world issues using various domains in cryptography, such as computer-aided cryptography and post-quantum cryptography. This included research on the HAPKIDO project about migrating PKI to post-quantum cryptography and a detailed post-quantum cryptography migration manual that covers technical and organisational requirements. In HAPKIDO, I implemented ITU-T X.509 compliant hybrid certificates. We frequently collaborated with different departments and companies to employ other topics such as machine-learning to our projects.}
    \end{cvitems}
  }
  \cventry
  {Junior Side Channel Analyst}
  {Brightsight B.V}
  {Delft, Netherlands}
  {Sep. 2020 - Jun. 2021}
  {
    \begin{cvitems}
      \item{Worked with in-house tools to perform various forms of side-channel attacks such as DPA, CPA, TA and deep-learning to break real-world systems. A report is then written describing and analysing the attack and its outcome.}
    \end{cvitems}
  }

  %\cventry
  %  {Tutor}
  %  {MyTutor}
  %  {MyTutor.co.uk}
  %  {Feb. 2017 - Apr. 2017 and Jan. 2019 - Sep. 2019}
  %  {
  %    \begin{cvitems}
  %     \item {Tutored A Level, GCSE and International Baccalaureate students in Computer %Science}
  %    \end{cvitems}
  %  }

  \cventry
  {IT Security Graduate}
  {Arm}
  {Cambridge, UK}
  {Sep. 2019 - Jul. 2020}
  {
    \begin{cvitems}
      \item{Worked in the Vulnerability Management team, where I automated processes such as producing scorecards to further understand and prioritise vulnerabilities identified in Arm's infrastructure, applications and web applications. Also worked in the Enterprise Security Architecture team, where I helped write and develop security requirements for various domains across Arm and visualise these requirements.}
    \end{cvitems}
  }

  %\cventry
  %  {Tutor}
  %  {MyTutor}
  %  {MyTutor.co.uk}
  %  {Feb. 2017 - Apr. 2017 and Jan. 2019 - Sep. 2019}
  %  {
  %    \begin{cvitems}
  %     \item {Tutored A Level, GCSE and International Baccalaureate students in Computer %Science}
  %    \end{cvitems}
  %  }
  \cventry
  {Teacher}
  {Happy Code}
  {Carcavelos, Portugal}
  {Apr. 2018 - Sep. 2019}
  {
    \begin{cvitems}
      \item {Taught weekly app development using MIT App Inventor 2 to children between the ages of 10 and 12 as well as Minecraft modding to children between the ages of 6 and 10. In these particularly difficult age groups, I managed to spark their interest in computer science and encouraged further learning at home.}
    \end{cvitems}
  }
  %  \cventry
  %    {Bar Staff}
  %%    {Bath Rugby}
  %  {Bath, United Kingdom}
  %  {Sep. 2017 - Jul. 2018}
  %  {
  %    \begin{cvitems}
  %     \item {Worked at the till, poured and served various kinds of drinks to rugby %spectators.}
  %    \end{cvitems}}

  \cventry
  {Intern}
  {CERN}
  {Geneva, Switzerland}
  {Jun. 2013}
  {
    \begin{cvitems}
      \item {Watched presentations about Computer Security and met with the Deputy Computer Security Officer who explained to me the details of his job. Also followed web tutorials on Python and configured Linux laptops}
    \end{cvitems}
  }
\end{cventries}